Numerical trajectory patterns of floating macroalgae

### 2020-10-02 thesis_chapter_3.Rmd
updated html. added to figures

---
title: 'Numerical trajectory patterns of floating macroalgae'
author: "Ross Coppin"
output:
  word_document:
    reference_docx: markdown/thesis_template.docx
  html_document:
  pdf_document:
    fig_caption: yes
bibliography: references.bib
csl: markdown/frontiers.csl.txt
---

@@

```{r data, message=FALSE, warning=FALSE, include=FALSE}

@@

p_RK4 <- tidync("OceanParcels/trajectory_data/PassiveFloat.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2002-01-01 00:00:00"))

@@

p_EE <- tidync("OceanParcels/trajectory_data/PassiveFloat.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2002-01-01 00:00:00"))

@@

k_app1_mean <- k_app2 %>% # summarise data based on time 
   group_by(t) %>% 
   summarise_all(funs(mean = mean, sd = sd, min = min, max = max), na.rm = T)

@@

total_data <- rbind(p_RK4, k_app1, k_app2)

@@

@@

heatmap_RK4 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_bin2d(data = k_app1, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

@@

heatmap_APP2 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

## Scatterplots

total_traj <- ggplot(data = total_data, aes(x = lon, y = lat, colour = type)) + 
  geom_point() + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  theme_bw() +
  guides(colour=guide_legend(title="Particle type"))

@@

library(ggpubr)
plot(total_traj)
ggarrange(heatmap_RK4,heatmap_APP1, heatmap_APP2, labels = c("A","B","C"), common.legend = TRUE, legend = c("right"))

>>>>

---
title: 'Numerical trajectory patterns of floating macroalgae'
author: "Ross Coppin"
output:
  html_document:
  word_document:
    reference_docx: markdown/thesis_template.docx
  pdf_document:
    fig_caption: yes
bibliography: references.bib
csl: markdown/frontiers.csl.txt
---

@@

```{r data wrangling, message=FALSE, warning=FALSE, include=FALSE}

@@

p_RK4 <- tidync("OceanParcels/trajectory_data/PassiveFloatRK4.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2002-01-01 00:00:00"))

@@

p_EE <- tidync("OceanParcels/trajectory_data/PassiveFloatEE.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2002-01-01 00:00:00"))

@@

k_app2_mean <- k_app2 %>% # summarise data based on time 
   group_by(t) %>% 
   summarise_all(funs(mean = mean, sd = sd, min = min, max = max), na.rm = T)

@@

total_data <- rbind(p_RK4, p_EE, k_app1, k_app2)

```{r scatter advection, message=FALSE, warning=FALSE, include=TRUE, echo=FALSE}

total_traj <- ggplot(data = total_data, aes(x = lon, y = lat, colour = type)) + 
  geom_point(aes(alpha = 0.2)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  theme_bw() +
  guides(colour=guide_legend(title="Particle type"))
total_traj

@@

bin_RK4 <- ggplot(p_EE, aes(x=lon, y=lat)) +
  geom_bin2d(bins = 20) +
  scale_fill_continuous(type = "viridis") +
  coord_fixed() +
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

@@

heatmap_RK4 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_bin2d(data = p_RK4, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

heatmap_EE <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_bin2d(data = p_EE, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw()

@@

heatmap_APP2 <- ggplot() +
  geom_polygon(data = south_africa_coast_hi_res, aes(x = lon, y = lat, group = PID),
               size = 1.0, colour = "black", fill = NA) +
  geom_bin2d(data = k_app2, bins = 80, aes(x = lon, y = lat)) +
  scale_fill_continuous(type = "viridis", limits = c(1, 13000)) +
  coord_cartesian(xlim = c(14, 20), ylim = c(-35, -30)) + 
  xlab("Longtitude") + 
  ylab("Latitude") + 
  guides(fill=guide_legend(title="Number of particles")) +
  theme_bw() 
```

@@

library(ggpubr)
ggarrange(heatmap_RK4, heatmap_EE, heatmap_APP1, heatmap_APP2, labels = c("A","B","C","D"), common.legend = TRUE, legend = c("right"))
